coDoc: A Tool for Managing Relationships between Codes and Documents

### 2013-02-14 P4-5-page-paper/paper.tex
backup

% This should NOT be raw data or code listings.  Instead you should present the key arch from your work.  Be guided by the papers you have read this quarter - in cases where it is necessary for understanding, a small section of code might be listed, separate from the text, but more commonly an algorithm might be shown.  Result are not long tables of data, rather, one or two graphs, or tables with key rows or columns highlighted or italicized.
\section{Architecture and Features of coDoc}
\label{sec:arch}
The result for the experiment is shown in fig.

>>>>

% This should NOT be raw data or code listings.  Instead you should present the key arch from your work.  Be guided by the papers you have read this quarter - in cases where it is necessary for understanding, a small section of code might be listed, separate from the text, but more commonly an algorithm might be shown.  Result are not long tables of data, rather, one or two graphs, or tables with key rows or columns highlighted or italicized.
\section{Architecture and Features of coDoc}
\label{sec:arch}

\begin{figure}
\begin{center}
\includegraphics[width=0.55\textwidth]{architecture.eps}
\caption{coDoc Architecture and Features}
\label{fig:architecture}
\end{center}
\end{figure}

The architecture of coDoc is shown in Figure \ref{fig:architecture}. 
It contains CDT editor, poppler, PDF editor and multi-editor.
There are three kinds of data here, 1) the codes, 2) the documents, 3) the relationships.
We only handle C/C++ code at this time, 
as most system code are written in this language.
CDT editor reads and parses the codes, 
highlights syntax elements.
We use poppler to read the pdf file and render the pdf pages to images.
As poppler is developed in C++, and Eclipse RCP is in Java language,
we need a adaptor to bridge the C++ code and the Java code.
We use JNI to implement this adaptor.
PDF editor implements an adaptor, 
and use it to get the PDF page from poppler and display it.
The multi-editor is responsible to read the relationship data,
and highlight certain code piece and document piece respectively.

To represent a relationship, 
we first need to define the strategy to identify the code piece and document piece.
As

% convert platformview.png platformview.eps
\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{platformview.eps}
\caption{coDoc Platform View}
\label{fig:platformview}
\end{center}
\end{figure}
